Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-05-07 ms.Rmd
Updated results with tables we can move to supplement

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, latex2exp, png, cowplot, magick, jpeg, clubSandwich)
source("./R/func.R")

@@

  # Get ANOVA stats for reporting in the paper of interaction
  anova_predators_inter <- anova(PredatorAC_inter)

# No support for an interaction. Drop interaction and fit the main effects model. Tells us that predation, regardless of whether we are talking about snakes or birds is just low in Hawaii, otherwise, we would predict that signals would evolve to match the predatory system

@@

  # Grab the ANOVA summary stats
    anova_predators <- anova(PredatorAC)

@@

     # Contrasts hypothesis tests, but use RVE 
    result_pred <- Wald_test(PredatorAC_pred_pop, constraints = constrain_pairwise(c(1:4)), vcov="CR2", tidy = TRUE)
    result_pred$p_val_bonfer <- sapply(p.adjust(result_pred$p_val, "bonferroni"), function(x) p_value(x))

@@

  # Doesn't look like an interaction, so test.
  anova(DispBgrdAC_inter, DispBgrdAC)

@@

  # Add Wald test to test signifiacnce of each factor, background and population using roust variance
  background_AC_Disp <- Wald_test(DispBgrdAC, constraints = constrain_zero(3), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

@@

    # Looks like weak evidence for interaction    
        anova(DispBgrdCC_inter, DispBgrdCC)

@@

```{r table1, tab.cap = "Model estimates, standard errors (SE), Saitterwaite degrees of freedom (df) and 95% confidence internals (95% CI) comparing acromatic and chromatic mean differences between Kenyan and Hawaiian lizards in two social contexts (Male-Male Competition and Courtship). Standard errors are corrected by using robust variance estimators. "}

@@

```{r table2, tab.cap = ""Model estimates, standard errors (SE), Saitterwaite degrees of freedom (df) and 95% confidence internals (95% CI) comparing acromatic and chromatic mean differences between Kenyan and Hawaiian lizards for snakes and lizards. Full models are provided and standard errors are corrected by using robust variance estimators."}

@@

CI_hyp_test

>>>>

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, latex2exp, png, cowplot, magick, jpeg, clubSandwich, flextable)
source("./R/func.R")

@@

@@

@@

     # Contrasts hypothesis tests, but use RVE

      PredatorAC_pred_pop <- lmer(dL ~  0+ pred_pop + (1|ID), data = Predator) 
    result_pred <- Wald_test(PredatorAC_pred_pop, constraints = constrain_pairwise(c(1:4)), 
                             vcov="CR2", tidy = TRUE)
    result_pred$p_val_bonfer <- sapply(p.adjust(result_pred$p_val, "bonferroni"), function(x) p_value(x))

@@

  # Doesn't look like an interaction, so test.
  inter_AC_Disp <- Wald_test(DispBgrdAC_inter, constraints = constrain_zero(4), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

@@

  # Add Wald test to test signifiacnce of each factor, background and population using roust variance

  background_AC_Disp <- Wald_test(DispBgrdAC, constraints = constrain_zero(3), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

@@

    # Doesn't look like an interaction, so test.
          inter_CC_Disp <- Wald_test(DispBgrdCC_inter, constraints = constrain_zero(4), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

@@

```{r table1, fig.width = 8, fig.height = 1, fig.asp = 0.1136364, tab.cap = "Model estimates, standard errors (SE), Saitterwaite degrees of freedom (df) and 95% confidence internals (95% CI) comparing acromatic and chromatic mean differences between Kenyan and Hawaiian lizards in two social contexts (Male-Male Competition and Courtship). Standard errors are corrected by using robust variance estimators. "}

@@

```{r table2, fig.width = 8, fig.height = 1, fig.asp = 0.1136364, tab.cap = "Model estimates, standard errors (SE), Saitterwaite degrees of freedom (df) and 95% confidence internals (95% CI) comparing acromatic and chromatic mean differences between Kenyan and Hawaiian lizards for snakes and lizards. Full models are provided and standard errors are corrected by using robust variance estimators."}

@@

```{r table3, fig.width = 9, fig.height = 1, fig.asp = 0.1136364, tab.cap = "Mean differences between Hawaiian and Kenyan visual signals for snake and bird predators."}

contrast <- rbind(CI_hyp_test,
                 CI_hyp_testAC)

contrast <- contrast %>% mutate(VisualSpec = c("Achromatic Contrast", "", "Chromatic Contrast", ""),
                                p_val = sapply(p_val, function(x) p_value(x))) %>% 
            select(VisualSpec, comparison, Estimate, lwr, upr, Fstat, df, p_val, p_bonf)

table3 <- flextable(contrast) %>% table_style8()
table3
```
